### 2008-09-08 doc/client/client_technical.tex
Getting there

\chapter{Implementation}
\label{sec:Implementation}
Clever text here.
\section{Generic Classes}
\subsection{{\ACC}}
The Arc Client Component ({\ACC}) class is a completely empty base class needed for the {\Loader} 
in order to create loadable classes.

@@

in any supported formats (currently xRSL, JDL, JSDL), converts and stores it in a JSDL-like internal job description format. The identification 
of the source's description format is internally handled by a \texttt{JobDescriptionOrderer} class which identifies the format by pattern
matching.

@@

\begin{enumerate}
\item{Try reading system configuration from \texttt{<ARC Install Location>/etc/arcclient.xml}}
\item{If the previous step failed try reading system configuration from \texttt{/etc/arcclient.xml}}
\item{Merge system and user configuration by adding all system configuration not already listed 
in the user configuration to the latter.}
\item{Check if \texttt{\$X509\_USER\_PROXY} is set, if set add this as \texttt{ProxyPath} to configuration}
\item{If \texttt{\$X509\_USER\_PROXY} is not set and configuration tree does not already contain 
a \texttt{ProxyPath} set \texttt{ProxyPath} to \texttt{/tmp/x509up\_u + userid}.}
\item{Check if \texttt{\$X509\_USER\_CERT} is set, if set add this as \texttt{CertificatePath} to configuration}
\item{If \texttt{\$X509\_USER\_CERT} is not set and configuration tree does not already contain 
a \texttt{CertificatePath} set \texttt{CertificatePath} to \texttt{/etc/grid-security/hostcert.pem} 
if user is superuser otherwise 
\texttt{\$HOME/.globus/usercert.pem}.}
\item{Check if \texttt{\$X509\_USER\_KEY} is set, if set add this as \texttt{KeyPath} to configuration}
\item{If \texttt{\$X509\_USER\_KEY} is not set and configuration tree does not already contain 
a \texttt{KeyPath} set \texttt{KeyPath} to \texttt{/etc/grid-security/hostkey.pem} 
if user is superuser otherwise \texttt{\$HOME/.globus/userkey.pem}.}
\item{Check if \texttt{\$X509\_CERT\_DIR} is set, if set add this as \texttt{CACertificatesDir} to configuration}
\item{If \texttt{\$X509\_CERT\_DIR} is not set and configuration tree does not already contain 
a \texttt{CACertificatesDir} set \texttt{CACertificatesDir} to \texttt{/etc/grid-security/certificates}.}
\end{enumerate}

@@

\section{Support Classes}
\subsection{{\URL}}
\subsection{Logger}
\subsection{XMLNode}

\chapter{Building Command Line Interfaces}
\label{sec:cli}

>>>>

\chapter{Implementation}
\label{sec:Implementation}
In this section an overview of all important classes in the new ARC1lib is given. The overview is subdivided in two 
parts where first all the generic classes are presented, Section~\ref{sec:genclass}, before the grid flavour specializations 
are presented in Section~\ref{sec:plugins}. Classes are described both in words and by code.

\section{Generic Classes}
\label{sec:genclass}
\subsection{{\ACC}}
The Arc Client Component ({\ACC}) class is a completely empty base class needed for the {\Loader} 
in order to create loadable classes.

@@

in any supported formats (currently xRSL~\cite{xrsl}, JDL~\cite{jdl}, JSDL~\cite{jsdl}), converts and stores it in a JSDL-like internal job description format. The identification 
of the source's description format is internally handled by a \texttt{JobDescriptionOrderer} class which identifies the format by pattern
matching.

@@

\begin{enumerate}
\item{Try reading system configuration from \texttt{<ARC Install Location>/etc/arcclient.xml}}
\item{If the previous step failed try reading system configuration from \texttt{/etc/arcclient.xml}}
\item{Merge system and user configuration by adding all system configuration not already listed 
in the user configuration to the latter.}
\item{Check if \texttt{\$X509\_USER\_PROXY} is set, if set add this as \texttt{ProxyPath} to configuration}
\item{If \texttt{\$X509\_USER\_PROXY} is not set and configuration tree does not already contain 
a \texttt{ProxyPath} set \texttt{ProxyPath} to \texttt{/tmp/x509up\_u + userid}.}
\item{Check if \texttt{\$X509\_USER\_CERT} is set, if set add this as \texttt{CertificatePath} to configuration}
\item{If \texttt{\$X509\_USER\_CERT} is not set and configuration tree does not already contain 
a \texttt{CertificatePath} set \texttt{CertificatePath} to \texttt{/etc/grid-security/hostcert.pem} 
if user is superuser otherwise \newline
\texttt{\$HOME/.globus/usercert.pem}.}
\item{Check if \texttt{\$X509\_USER\_KEY} is set, if set add this as \texttt{KeyPath} to configuration}
\item{If \texttt{\$X509\_USER\_KEY} is not set and configuration tree does not already contain 
a \texttt{KeyPath} set \texttt{KeyPath} to \texttt{/etc/grid-security/hostkey.pem}
if user is superuser otherwise \texttt{\$HOME/.globus/userkey.pem}.}
\item{Check if \texttt{\$X509\_CERT\_DIR} is set, if set add this as \texttt{CACertificatesDir} to configuration}
\item{If \texttt{\$X509\_CERT\_DIR} is not set and configuration tree does not already contain 
a \texttt{CACertificatesDir} set \texttt{CACertificatesDir} to \texttt{/etc/grid-security/certificates}.}
\end{enumerate}

@@

\chapter{Building Command Line Interfaces}
\label{sec:cli}
Given all components listed above it possible to write versatile command line interfaces (cli) for 
grid job submission and management. ARC1lib offers the following native commands:

\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status queries.}
\item{\texttt{arcsub} - for grid job submission}
\item{\texttt{arcget} - for downloading output of finished, cancelled or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory including all contents}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a running grid job's std out or std error file.}
\end{enumerate}

Each of the commands above are encoded within one C++ file with the following structure:

\begin{shaded}
\begin{verbatim}
#ifdef HAVE_CONFIG_H
#include <config.h>
#endif

#include <arc/ArcLocation.h>
#include <arc/IString.h>
#include <arc/Logger.h>
#include <arc/OptionParser.h>
#include <arc/client/UserConfig.h>
#include <arc/IString.h>

void MyCommand(MyArgument1,
               MyArgument2){

  //Implementation of MyCommand

}

int main(int argc, char **argv){

  setlocale(LC_ALL, "");

  Arc::LogStream logcerr(std::cerr);
  Arc::Logger::getRootLogger().addDestination(logcerr);
  Arc::Logger::getRootLogger().setThreshold(Arc::WARNING);

  Arc::ArcLocation::Init(argv[0]);

  Arc::OptionParser options(istring("argument"), "", istring(
                              "Clarifying text here));

  //add command options
  bool all = false;
  options.AddOption('a', "all",
		    istring("all jobs"),
		    all);

  std::list<std::string> params = options.Parse(argc, argv);

  //call command
  MyCommand(all, params);

  return 0;

}
\end{verbatim}
\end{shaded}

The structure above has two separate blocks of code where the first block is the MyCommand method which is be 
called by the main program (second block). Certainly this is not the only way of building (structuring) a 
command line interface, but it has the benefit of a clear structure in addition to that the method implemented 
can easily be reused in a different location without code duplication.
